Titeln på avhandlingens språk

### 2022-08-24 model.tex
writing

\emph{Execution time} and \emph{time-to-feedback} correspond to the two key metrics necessary to characterize the interactions between system responsiveness and human behavior.

>>>>

\emph{Execution time} and \emph{time-to-feedback} correspond to the two key metrics necessary to characterize the interactions between human behavior and system responsiveness.
